SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-26 scipy-1.0/paper.tex
Add a brief description of the compatibility policies used in determining which LAPACK routines can have Cython wrappers. Also mention why there aren't similar concerns for the BLAS and special wrappers.

>>>>

Since SciPy can be built with LAPACK 3.4.0 or later, Cython wrappers are only provided for the routines that maintain a consistent interface across all supported LAPACK versions.
In other words, wrappers are provided for routines that are included in the earliest supported LAPACK version and are not removed or changed in some incompatible way in some subsequent LAPACK release.
The standard BLAS interface provided by the various existing BLAS libraries is not currently changing, so changes are not generally needed in the wrappers we provide.
Changes to the Cython wrappers for the functions in \texttt{scipy.{\allowbreak}special} follow corresponding changes to the interface of that submodule.
